\Large \bf \vrsdust{0.7cm} \hspace{0.1in} Redstone: a Deterministic Simulation Testing Framework for Distributed Systems

### 2024-06-08 paper/paper.tex
Edited determinism section

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
{\fontsize{12}{15}\selectfont 
In testing distributed systems,
confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
Redstone, a deterministic simulation testing framework,
amplifies failures in various substrates underlying a distributed system
in order to confirm the system's ability to withstand these failures.
We intercept calls to the kernel for the disk and the network, as well as to clock functions,
introducing our own code. Our control over clock functions further allows us to ``accelerate" time,
increasing ability to test faster, and to emulate the effects of clock jitter. Additionally, our framework has been made modular to be easily implemented alongside nearly any distributed system for the sake of enabling testing a breadth of distributed systems. Most importantly, though, Redstone's
determinism allows reproduction of failure conditions,
allowing developers to confirm, having encountered and debugged a failure,
that their system will not fail again when confronted by identical conditions. By basing program flow on a pre-chosen seed, any found faults, no matter how improbable, can be reliably replicated. We implement and evaluate our framework on a simple system in Linux to demonstrate this determinism in practice.

@@

{\fontsize{12}{15}\selectfont

The core of the simulated testing framework is its randomness. By introducing randomness into whether or not a network packet is dropped or replayed, for example, the system is able to cover a breadth of inputs that are harder to anticipate when designing the distributed system. Many of these inputs will inevitably cause failures in the distributed system due to lack of cases covered by the distributed system itself. The whole purpose of distributed systems testing frameworks is to find these cases. The primary goal of Redstone though is, in addition to revealing these cases, make it simple to be able to deterministically find these “random” cases. The method by which Redstone seeks to do so is by introducing a seed. The seed is chosen before the simulator runs by the user. Then, rather whenever a random number is called in the simulation (say, 0 if a packet should be dropped or 1 if a packet should be allowed through), the value can be pseudo randomly generated based on the seed. Thus, the system covers a “random” program flow that can easily be iterated on. When an interesting program flow is discovered by the user, logs are played that cover what occurred during the run. However, instead of having to do the analysis entirely in post, the user can take note of the seed with which the simulation was run and simply run it again. Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two, the user can expect the exact same program flow to execute and to reproduce the same logs live. Between these logs and the replicability of the program flow results, the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.

@@

\section{\txtrsdust Evaluations}

{\fontsize{12}{15}\selectfont

This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.

@@

{\fontsize{12}{15}\selectfont

Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.

// Talk about limitations, otherwise desired future plans/potential future work

@@

% Distributed systems are fucking stupid.
% 
% Therefore, in order to combat this stupidity, there was the advent of a concept of "testing".
% This dark and arcane art is wonderfully usable but falls flat when tested conditions occur only
% rarely. The best example of such wild conditions are things like network latencies, disk
% io errors, kernel bugs, time, and more. Everything has some level of doing a fucky wucky,
% so our job is to make these fucky wuckies happen more often so that programmers are better able to
% understand how their system handles such fucky wuckies
% A paragraph of text goes here. Lots of text. Plenty of interesting
% text. Text text text text text text text text text text text text text
% text text text text text text text text text text text text text text
% text text text text text text text text text text text text text text
% text text text text text text text.
% More fascinating text. Features galore, plethora of promises.

% %-------------------------------------------------------------------------------
% \section{Footnotes, Verbatim, and Citations}
% %-------------------------------------------------------------------------------
% 
% Footnotes should be places after punctuation characters, without any
% spaces between said characters and footnotes, like so.%
% \footnote{Remember that USENIX format stopped using endnotes and is
% now using regular footnotes.} And some embedded literal code may
% look as follows.
% 
% \begin{verbatim}
% int main(int argc, char *argv[]) 
% {
% return 0;
% }
% \end{verbatim}
% 
% Now we're going to cite somebody. Watch for the cite tag. Here it
% comes. Arpachi-Dusseau and Arpachi-Dusseau co-authored an excellent OS
% book, which is also really funny~\cite{arpachiDusseau18:osbook}, and
% Waldspurger got into the SIGOPS hall-of-fame due to his seminal paper
% about resource management in the ESX hypervisor~\cite{waldspurger02}.
% 
% The tilde character (\~{}) in the tex source means a non-breaking
% space. This way, your reference will always be attached to the word
% that preceded it, instead of going to the next line.
% 
% And the 'cite' package sorts your citations by their numerical order
% of the corresponding references at the end of the paper, ridding you
% from the need to notice that, e.g, ``Waldspurger'' appears after
% ``Arpachi-Dusseau'' when sorting references
% alphabetically~\cite{waldspurger02,arpachiDusseau18:osbook}. 
% 
% It'd be nice and thoughtful of you to include a suitable link in each
% and every bibtex entry that you use in your submission, to allow
% reviewers (and other readers) to easily get to the cited work, as is
% done in all entries found in the References section of this document.
% 
% Now we're going take a look at Section~\ref{sec:figs}, but not before
% observing that refs to sections and citations and such are colored and
% clickable in the PDF because of the packages we've included.
% 
% %-------------------------------------------------------------------------------
% \section{Floating Figures and Lists}
% \label{sec:figs}
% %-------------------------------------------------------------------------------

% %---------------------------
% \begin{figure}
% \begin{center}
% \begin{tikzpicture}
% \draw[thin,gray!40] (-2,-2) grid (2,2);
% \draw[<->] (-2,0)--(2,0) node[right]{$x$};
% \draw[<->] (0,-2)--(0,2) node[above]{$y$};
% \draw[line width=2pt,blue,-stealth](0,0)--(1,1)
% node[anchor=south west]{$\boldsymbol{u}$};
% \draw[line width=2pt,red,-stealth](0,0)--(-1,-1)
% node[anchor=north east]{$\boldsymbol{-u}$};
% \end{tikzpicture}
% \end{center}
% \caption{\label{fig:vectors} Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. Text size inside figure should be as big as
% caption's text. }
% \end{figure}
% %% %---------------------------

% Here's a typical reference to a floating figure:
% Figure~\ref{fig:vectors}. Floats should usually be placed where latex
% wants then. Figure\ref{fig:vectors} is centered, and has a caption
% that instructs you to make sure that the size of the text within the
% figures that you use is as big as (or bigger than) the size of the
% text in the caption of the figures. Please do. Really.
% 
% In our case, we've explicitly drawn the figure inlined in latex, to
% allow this tex file to cleanly compile. But usually, your figures will
% reside in some file.pdf, and you'd include them in your document
% with, say, \textbackslash{}includegraphics.
% 
% Lists are sometimes quite handy. If you want to itemize things, feel
% free:
% 
% \begin{description}
% 
% \item[fread] a function that reads from a \texttt{stream} into the
% array \texttt{ptr} at most \texttt{nobj} objects of size
% \texttt{size}, returning returns the number of objects read.
% 
% \item[Fred] a person's name, e.g., there once was a dude named Fred
% who separated usenix.sty from this file to allow for easy
% inclusion.
% \end{description}
% 
% \noindent
% The noindent at the start of this paragraph in its tex version makes
% it clear that it's a continuation of the preceding paragraph, as
% opposed to a new paragraph in its own right.
% 
% 
% \subsection{LaTeX-ing Your TeX File}
% %-----------------------------------
% 
% People often use \texttt{pdflatex} these days for creating pdf-s from
% tex files via the shell. And \texttt{bibtex}, of course. Works for us.

%-------------------------------------------------------------------------------
\section*{Acknowledgments}
%-------------------------------------------------------------------------------

The USENIX latex style is old and very tired, which is why
there's no \textbackslash{}acks command for you to use when
acknowledging. Sorry.

%-------------------------------------------------------------------------------
\section*{Availability}
%-------------------------------------------------------------------------------

USENIX program committees give extra points to submissions that are
backed by artifacts that are publicly available. If you made your code
or data available, it's worth mentioning this fact in a dedicated
section.

>>>>

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
{\fontsize{12}{15}\selectfont 
In testing distributed systems,
confirming a system's tolerance of faults in disks and networks is not only useful but necessary.
Redstone, a deterministic simulation testing framework,
amplifies failures in various substrates underlying a distributed system
in order to confirm the system's ability to withstand these failures.
We intercept calls to the kernel for the disk and the network, as well as to clock functions,
introducing our own code. Our control over clock functions further allows us to
``accelerate'' time, %NOTE: what the fuck
increasing ability to test faster, and to emulate the effects of clock jitter. Additionally, our framework has been made modular to be easily implemented alongside nearly any distributed system for the sake of enabling testing a breadth of distributed systems. Most importantly, though, Redstone's
determinism allows reproduction of failure conditions,
allowing developers to confirm, having encountered and debugged a failure,
that their system will not fail again when confronted by identical conditions. By basing program flow on a pre-chosen seed, any found faults, no matter how improbable, can be reliably replicated. We implement and evaluate our framework on a simple system in Linux to demonstrate this determinism in practice.

@@

{\fontsize{12}{15}\selectfont 
The core of the simulated testing framework is its test injection.
By introducing randomness into whether or not a network packet is dropped or replayed,
for example, the system is able to cover a breadth of ``environmental conditions",
so to speak,
that are harder to anticipate when designing the distributed system.

Many of these ``environmental conditions"
will inevitably cause failures in the distributed system due to insufficient edge case handling by the implementers of the system.
This is a feature, not a bug.
The whole purpose of distributed systems testing frameworks is to find these cases.

The primary goal of Redstone, however,
in addition to revealing these cases,
is to make it simple to be able to deterministically find these “random” cases.
The method by which Redstone seeks to do so is by introducing a seed.

The seed is chosen by the user before the simulator runs.
Wherever randomness is necessary
% Then, rather whenever a random number is called in the simulation
(say, to determine whether a packet should be dropped),
the value can be pseudo-randomly generated based on the seed.

Thus, the system performs a ``random" and yet totally deterministic program flow,
which can be used in development for iteration on the tested system.
When an interesting program flow is discovered by the user,
instead of just relying on logs after the fact,
the user can take note of the seed with which the simulation was run and simply run it again.

Due to the guarantees provided by the seed, the execution of the program flow, and the interactions between the two,
the user can expect the exact same program flow to execute and to reproduce the same sequence of events as the one they see in their logs.
Between these logs and the replicability of the program flow results,
the user is able to get the randomness desired of a distributed system testing framework as well as the determinism required to understand and replay the results.

@@

\section{\txtrsdust Evaluation}

{\fontsize{12}{15}\selectfont 
\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
% This section needs: at least 1 graph/table, explanations of what we evaluated and how, what the evaluation tells us.

@@

{\fontsize{12}{15}\selectfont 
\texttt{NOTE: we are in the process of writing up this section, and will submit this in an amended version of the writeup tomorrow morning.}
% Based on our results, we find the Redstone framework promising in its ability to deterministically replay results.

% // Talk about limitations, otherwise desired future plans/potential future work

@@

% Distributed systems are fucking stupid.
% 
% Therefore, in order to combat this stupidity, there was the advent of a concept of "testing".
% This dark and arcane art is wonderfully usable but falls flat when tested conditions occur only
% rarely. The best example of such wild conditions are things like network latencies, disk
% io errors, kernel bugs, time, and more. Everything has some level of doing a fucky wucky,
% so our job is to make these fucky wuckies happen more often so that programmers are better able to
% understand how their system handles such fucky wuckies

% %-------------------------------------------------------------------------------
% \section*{Acknowledgments}
% %-------------------------------------------------------------------------------
% 
% The USENIX latex style is old and very tired, which is why
% there's no \textbackslash{}acks command for you to use when
% acknowledging. Sorry.
% 
% %-------------------------------------------------------------------------------
% \section*{Availability}
% %-------------------------------------------------------------------------------
% 
% USENIX program committees give extra points to submissions that are
% backed by artifacts that are publicly available. If you made your code
% or data available, it's worth mentioning this fact in a dedicated
% section.
